Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-11 main_paper.tex

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT and the Wild bootstrap
uses the ``HC3'' transformation of \citet{DF08}. We also estimate CCT's bias
corrected procedure with AMSE-optimal bandwidths and
the uniform kernel for direct comparison.

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap interval and ``CCT'' shows
results for the analytically-corrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each interval.
In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
our proposed bootstrap procedure has coverage about one percentage lower than the CCT's analytical counterpart. In Panel B, the coverage is very similar to Panel A, showing that both procedures are robust to heteroskedasticity.
The final column, ``CI Length,'' indicates that our proposed bootstrap procedure consistently generates narrower intervals, in line with the coverage results.

>>>>

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs ($\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT and the Wild bootstrap
uses the ``HC3'' transformation of \citet{DF08}.

We include two other procedures for comparison: CCT's bias-corrected interval
and a ``naive'' uncorrected estimator, both using the triangular kernel. We
estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate
the ``naive'' uncorrected interval with the optimal bandwidth $h$ proposed by
\cite{IK}, and both use the HC3 variance estimator to facilitate comparisons
with the Wild bootstrap.\footnote{%
  Simulation results for other kernels and variance estimators are similar and
  available upon request.} %

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap interval; ``CCT'' shows
results for the analytically-corrected interval and ``Naive'' shows results for analytically-uncorrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each interval.  In
Panel A, all of the intervals from two robust estimators are reasonably close to
their nominal coverage, although they slightly under cover the true treatment
effect. The uncorrected intervals perform substantially worse---the naive
analytical interval has coverage as bad as 35\% (in the second DGP) and never
higher than 86\%. In Panel B, the coverage does not change too much from Panel
A. In presence of heteroskedasticity, the two robust procedures again perform
similarly and have coverage close to the nominal level. The final column, ``CI
Length,'' indicates that intervals from the two robust procedures have almost
the same length on average, while interval from the naive procedure has much
shorter length on average. Not surprisingly, the average length of intervals
from all three procedures increases when the data is heteroskedastic.
